---
title: "WordOrderStudy_plots"
author: "Amélie la Roi"
date: "March 23, 2020"
output: html_document
---

Last update: March 23, 2020

## Load required packages
```{r}
library(plyr)
library(itsadug)
library(mgcv)
library(ggplot2)

packageVersion('itsadug') # 2.3
packageVersion('mgcv') # 1.8.31
```

&nbsp;

## Load models
```{r}
print(load("./Models/ROI.m7REML.rda"))
print(load("./Models/ROI.m72REML.rda"))

```

&nbsp;

# Evaluate differences by plotting
## Plot time course of critword conditions over all ages
```{r fig.width=10, fig.height=5}
# Plot models
## Plot smooth per critword condition averaged over all participants
### Plot SOV and SVO sentences next to each other
par(mfrow=c(1,2))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.5, cex.main=2, legend_plot_all = "topright", ylim=c(-1.5,1.5), v=0) 

plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.5, cex.main=2, legend_plot_all = "topright", ylim=c(-1.5,1.5), v=0)
```

&nbsp;

## Plot smooth per critword condition in SOV sentences split out per decade
```{r fig.width=20, fig.height=10}
par(mfrow=c(2,4))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 20", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=20), ylim=c(-1.5,1.5)) # legend is plotted outside the plot to make it disappear
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 30", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=30), ylim=c(-1.5,1.5))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 40", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=40), ylim=c(-1.5,1.5))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 50", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=50), ylim=c(-1.5,1.5))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 60", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=60), ylim=c(-1.5,1.5))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 70", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=70), ylim=c(-1.5,1.5))
plot_smooth(ROI.m7REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SOV\nAge = 80", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all=list(x=350,y=1), cond=list(Age=80), ylim=c(-1.5,1.5))
```

&nbsp;

## Plot smooth per critword condition in SVO sentences split out per decade
```{r fig.width=20, fig.height=10}
par(mfrow=c(2,4))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 20", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=20), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 30", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=30), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 40", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=40), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 50", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=50), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 60", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=60), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 70", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all = list(x=-500,y=-5), cond=list(Age=70), ylim=c(-1.5,1.5))
plot_smooth(ROI.m72REML, view="Time", plot_all="critword", rm.ranef=TRUE, eegAxis = TRUE, n.grid=100, main="SVO\nAge = 80", col=c("green","blue","red"), cex.lab=1.5, cex.axis=1.7, cex.main=2, legend_plot_all=list(x=250,y=0.75), cond=list(Age=80), ylim=c(-1.5,1.5))
```

&nbsp;

## Plot difference between critword conditions over all ages
### In SOV and SVO sentences
```{r fig.width=15, fig.height=10}
## Plot one-dimensional difference smooths
par(mfrow=c(2,3))

# SOV sentences
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SOV\nUnrelated vs. correct", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SOV\nUnrelated vs. literal", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SOV\nLiteral vs. correct", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))

# SVO sentences
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SVO\nUnrelated vs. correct", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SVO\nUnrelated vs. literal", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="SVO\nLiteral vs. correct", cex.lab=2, cex.axis=2, cex.main=2, ylim=c(-1.5,1.5))

```

&nbsp;

# Plot differences between conditions in SOV sentences for different ages to:
# 1) Find out the time point at which differences between conditions differ from each other over age
# 2) Get insight in latencies of significant differences between conditions at different ages
```{r fig.width=20, fig.height=10}

# Unrelated vs. correct (significant till 56)
par(mfrow=c(2,4))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 

# Unrelated vs. literal (significant up to age 30)
par(mfrow=c(2,4))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))

# Literal vs. correct (no significant differences)
par(mfrow=c(2,4))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m7REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
```

&nbsp;

# Plot differences between conditions in SVO sentences for different ages to:
# 1) Find out the time point at which differences between conditions differ from each other over age
# 2) Get insight in latencies of significant differences between conditions at different ages
```{r fig.width=20, fig.height=10}

# Unrelated vs. correct (significant till 63)
par(mfrow=c(2,4))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "correct")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. correct\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5)) 

# Unrelated vs. literal (significant between 38-57)
par(mfrow=c(2,4))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("unrelated", "literal")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Unrelated vs. literal\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))

# Literal vs. correct (significant till 50 )
par(mfrow=c(2,4))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=20), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=20", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=30), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=30", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=40), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=40", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=50), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=50", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=60), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=60", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=70), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=70", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))
plot_diff(ROI.m72REML, view="Time", comp=list(critword=c("literal","correct")), cond=list(Age=80), rm.ranef=TRUE, eegAxis = TRUE, v=0, n.grid=100, main="Literal vs. correct\nAge=80", cex.lab=2.5, cex.axis=2.5, cex.main=2.5, ylim=c(-1.5,1.5))


```

&nbsp;

## Plot differences between critword conditions for interactions between Time and Age 
### For SOV and SVO sentences
```{r fig.width=15, fig.height=10}
# Plot difference surfaces SOV sentences
par(mfrow=c(2,3))
## Unrelated vs. correct
plot_diff2(ROI.m7REML, view=c("Time", "Age"), 
    comp=list(critword=c("unrelated", "correct")), 
    rm.ranef=TRUE, main="SOV\nUnrelated vs. correct",
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2) 

## Unrelated vs. literal
plot_diff2(ROI.m7REML, view=c("Time", "Age"), 
    comp=list(critword=c("unrelated", "literal")), 
    rm.ranef=TRUE, main="SOV\nUnrelated vs. literal",
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2) 

## Literal vs. correct
plot_diff2(ROI.m7REML, view=c("Time", "Age"), 
    comp=list(critword=c("literal","correct")), 
    rm.ranef=TRUE, main="SOV\nLiteral vs. correct",
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2) 

# Add difference surfaces Verb-second sentences
## Unrelated vs. correct
plot_diff2(ROI.m72REML, view=c("Time", "Age"), 
    comp=list(critword=c("unrelated", "correct")), 
    rm.ranef=TRUE, main="SVO\nUnrelated vs. correct", 
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2) 

## Unrelated vs. literal
plot_diff2(ROI.m72REML, view=c("Time", "Age"), 
    comp=list(critword=c("unrelated", "literal")), 
    rm.ranef=TRUE, main="SVO\nUnrelated vs. literal", 
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2) 

## Literal vs. correct
plot_diff2(ROI.m72REML, view=c("Time", "Age"), 
    comp=list(critword=c("literal","correct")), 
    rm.ranef=TRUE, main="SVO\nLiteral vs. correct", 
    color="terrain", zlim=c(-1.25,1), cex.lab=1.5, cex.axis=1.5, cex.main=2)

```

