---
title: "WordOrderStudy_GAMManalysis_SOV"
author: "Amélie la Roi"
date: "March 21, 2020"
output: html_document
---

Last update: February 5, 2021

## Load required packages
```{r}
library(plyr)
library(itsadug)
library(mgcv)
library(ggplot2)

packageVersion('itsadug') # 2.3
packageVersion('mgcv') # 1.8.31
```

&nbsp;

## Run GAMMs on mean voltage of ROI
### Compute subject means to include subject as random effect
```{r results='hide'}
datadir <- "./Preprocessing_persubject_epochICA/"
allfiles <- dir(path=datadir)
dat <- c()


# Load and save data from all participants for one electrode
for(i in allfiles ){
  print(i)
  load(sprintf("%s/%s", datadir, i))
  
  subdat <- droplevels(finalO[finalO$Electrode %in% c("C3","C1","Cz","C2","C4","CP3","CPz","CP4","Pz","P1","P2","P3","P4"),])
  dat <- rbind(dat, subdat)
  subdat <- NULL
}

# Compute mean amplitude change over time per subject and condition
subjectROI <- ddply(dat, c("Subject", "Age", "order", "critword", "Time"), summarise,
             subj.mV.median = median(mV, na.rm=TRUE),
             subj.mV = mean(mV, na.rm=TRUE),
             subj.mV = mean(mV, na.rm=TRUE),
             subj.n = length(mV[!is.na(mV)]))

```

&nbsp;

# GAMM analysis
## Prepare variables
```{r prepare variables}
# Make sure variables are factors
subjectROI$Subject <- as.factor(subjectROI$Subject)
subjectROI$order <- as.factor(subjectROI$order)
subjectROI$critword <- as.factor(subjectROI$critword)
subjectROI$Event <- interaction(subjectROI$Subject, subjectROI$order, subjectROI$critword, drop=TRUE)

# Determine starting point for each time series
subjectROI <- start_event(subjectROI)

# Check number of data points to select gam (< 10000) or bam (> 10000)
dim(subjectROI) # more than 10000 data points, so use bam

# CREATE ORDERED FACTORS
## For critword conditions
subjectROI$CritCor <- as.ordered(subjectROI$critword == 'correct')
contrasts(subjectROI$CritCor) <- "contr.treatment"
subjectROI$CritLit <- as.ordered(subjectROI$critword == 'literal')
contrasts(subjectROI$CritLit) <- "contr.treatment"
subjectROI$CritUnrel <- as.ordered(subjectROI$critword == 'unrelated')
contrasts(subjectROI$CritUnrel) <- "contr.treatment"

# Create dataframe per sentence order
subjectROI_final <- droplevels(subjectROI[subjectROI$order == 'verb-final',])
subjectROI_first <- droplevels(subjectROI[subjectROI$order == 'verb-first',])

# Select data from -100 - 600 ms time window
subjectROI_finalE <- droplevels(subjectROI_final[subjectROI_final$Time >= -100 & subjectROI_final$Time < 600,])
subjectROI_firstE <- droplevels(subjectROI_first[subjectROI_first$Time >= -100 & subjectROI_first$Time < 600,])

# Redefine start_event
subjectROI_finalE <- start_event(subjectROI_finalE)
subjectROI_firstE <- start_event(subjectROI_firstE)

# Remove dataframes that will not be used for model fitting
rm(dat, subjectROI, subjectROI_first, subjectROI_final)

```

&nbsp;

## Model comparison with method="ML"
### *SOV SENTENCES*
```{r}
## Fit full model with method="ML"
if(FALSE){
ROI.m6REML <- bam( subj.mV ~ critword 
            + s(Time, k=40, by=critword) 
            + s(Age, by=critword) 
            + ti(Time, Age, k=c(40,5), by=critword)
           + s(Time, Event, bs="fs", m=1, k=20), # Event = interaction between subject and critword
           data=subjectROI_finalE, discrete = FALSE, method="ML",
           AR.start=subjectROI_finalE$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m6REML.rda"))}

# Model summary
summary(ROI.m6REML) # smooth over Age is not significantly different from zero

# Print model statistics
report_stats(ROI.m6REML)
```

&nbsp;

### Check contribution of smooth over Age
```{r}
## Fit model without smooth over Age (with method="ML")
if(FALSE){
ROI.m7REML <- bam( subj.mV ~ critword 
            + s(Time, k=40, by=critword) 
            + ti(Time, Age, k=c(40,5), by=critword)
            + s(Time, Event, bs="fs", m=1, k=20), 
           data=subjectROI_finalE, discrete = FALSE, method="ML",
           AR.start=subjectROI_finalE$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m7REML.rda"))}

# Model summary
summary(ROI.m7REML, re.test=FALSE)

# Compare models
compareML(ROI.m6REML, ROI.m7REML, suggest.report = TRUE)

# Remove model to free workspace
rm(ROI.m6REML)

```

&nbsp;

### Test effect of Operation Span score on SOV sentences
```{r}
# Load operation span data
print(load("./Cognitive scores/OS.PCU.rda"))

# Merge OS scores with EEG data
subjectROI_finalE.OS.PCU <- merge(OS.PCU2, subjectROI_finalE, by= "Subject")

save(subjectROI_finalE.OS.PCU, file="./R output/subjectROI_finalE.OS.PCU.rda", compress="xz")

# Plot scores on Operation Span task as a function of age
print(load("G:/Back-up Y-schijf 12.03.2020/Study 1 - EEG+priming task/Analysis/EEG/R output/subjectROI_finalE.OS.PCU.rda"))
plot(subjectROI_finalE.OS.PCU$subj.OS ~ subjectROI_finalE.OS.PCU$Age, main="Operation Span task", ylab="Operation Span score", xlab="Age")
abline(lm(subjectROI_finalE.OS.PCU$subj.OS ~ subjectROI_finalE.OS.PCU$Age))

# Fit model including smooth for operation span score
if(FALSE){
ROI.m8REML <- bam( subj.mV ~ critword 
            + s(Time, k=40, by=critword)
            + ti(Time, Age, k=c(40,5), by=critword)
            + s(subj.OS)
            + s(Time, Event, bs="fs", m=1, k=20), 
           data=subjectROI_finalE.OS.PCU, discrete = FALSE, method="ML",
           AR.start=subjectROI_finalE.OS.PCU$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m8REML.rda"))}

# Model summary
summary(ROI.m8REML, re.test=FALSE)

# Compare models
compareML(ROI.m8REML, ROI.m7REML, suggest.report = TRUE) # operation span score doesn't improve model fit

# Print statistics to report
report_stats(ROI.m8REML) # operation span score is not a significant predictor

# Remove model to free workspace
rm(ROI.m8REML)
```

&nbsp;

### Test effect of Numerical Stroop score on SOV sentences
```{r}
# Load numerical stroop data
print(load("./Cognitive scores/subjectStroop.rda"))

# Merge OS scores with EEG data
subjectROI_finalE.NS <- merge(subjectStroop, subjectROI_finalE, by= "Subject")

save(subjectROI_finalE.NS, file="./R output/subjectROI_finalE.NS.rda", compress="xz")

# Plot scores on Numerical Stroop task as a function of age
print(load("G:/Back-up Y-schijf 12.03.2020/Study 1 - EEG+priming task/Analysis/EEG/R output/subjectROI_finalE.NS.rda"))
plot(subjectROI_finalE.NS$Stroop ~ subjectROI_finalE.NS$Age, main="Numerical Stroop task", ylab="Numerical Stroop score in ms", xlab="Age")
abline(lm(subjectROI_finalE.NS$Stroop ~ subjectROI_finalE.NS$Age))

# Fit model with numerical stroop data
if(FALSE){
ROI.m9REML <- bam( subj.mV ~ critword 
            + s(Time, k=40, by=critword)
            + ti(Time, Age, k=c(40,5), by=critword)
            + s(Stroop)
            + s(Time, Event, bs="fs", m=1, k=20), 
           data=subjectROI_finalE.NS, discrete = FALSE, method="ML",
           AR.start=subjectROI_finalE.NS$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m9REML.rda"))}

# Model summary
summary(ROI.m9REML, re.test=FALSE)

# Compare models
compareML(ROI.m7REML, ROI.m9REML, suggest.report = TRUE) # numerical stroop score doesn't improve model fit

# Print statistics to report
report_stats(ROI.m9REML) # numerical stroop score is not a significant predictor

# Remove models to free workspace
rm(ROI.m7REML, ROI.m9REML)
```

&nbsp;

## Check differences between critword conditions 

In a model with binary predictors, the binary term can only be included once. If the binary terms occurs multiple times, the model doesn't know in which term the intercept difference should be included. In our design, we need to fit the same difference curves (modeling the differences between the critical word conditions) for the smooth over Time, the smooth over Age, and the interaction smooth over Time and Age. To be able to do this, we need to use ordered factors. With ordered factors, the intercept difference and nonlinear difference are captured in separate smooths. So in addition to giving us the possibility to fit the differences between critical word conditions in multiple smooths, ordered factors also provide insight in whether potential differences between critical word conditions arise from intercept differences or nonlinear differences.

### Fit model with ordered factors
```{r}
# Correct reference
if(FALSE){
ROI.m7REML.ordCor <- bam( subj.mV ~ CritLit + CritUnrel
              # reference curve         
              + s(Time, k=40) 
              # difference curves
              + s(Time, by=CritLit) + s(Time, by=CritUnrel) 
              # reference surface
              + ti(Time, Age)
              # difference surface
              + ti(Time, Age, k=c(40,5), by=CritLit) + ti(Time, Age, k=c(40,5), by=CritUnrel)
              + s(Time, Event, bs="fs", m=1, k=20), 
              data=subjectROI_finalE, discrete = FALSE, method="ML",
              AR.start=subjectROI_finalE$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m7REML.ordCor.rda"))
  }

# Print model summary
summary(ROI.m7REML.ordCor, re.test=FALSE)

# Print model statistics
report_stats(ROI.m7REML.ordCor)

# Remove model to free workspace
rm(ROI.m7REML.ordCor)

# Literal reference
if(FALSE){
ROI.m7REML.ordLit <- bam( subj.mV ~ CritCor + CritUnrel
              # reference curve         
              + s(Time, k=40)
              # difference curves
              + s(Time, by=CritCor) + s(Time, by=CritUnrel) 
              # reference surface
              + ti(Time, Age)
              # difference surface
              + ti(Time, Age, k=c(40,5), by=CritCor) + ti(Time, Age, k=c(40,5), by=CritUnrel)
              + s(Time, Event, bs="fs", m=1, k=20), 
              data=subjectROI_finalE, discrete = FALSE, method="ML",
              AR.start=subjectROI_finalE$start.event, rho=myrho1.ROIE)
}else{print(load("./Models/ROI.m7REML.ordLit.rda"))
  }

# Print model summary
summary(ROI.m7REML.ordLit, re.test=FALSE)

# Print model statistics
report_stats(ROI.m7REML.ordLit)

# Remove model to free workspace
rm(ROI.m7REML.ordLit)
```

