---
title: "WordOrderStudy_Preprocessing"
author: "Amélie la Roi"
date: "March 23, 2020"
output: html_document
---

Last update: March 23, 2020

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

&nbsp;

#### Load data
```{r}
# Load data with ICA on epochs
## Adapt command below for each participant
data <- read.delim("./Analysis data_epochICA/epochICA_eeg_32.txt", header = T)

# Rename column
colnames(data)[1] <- "Time" # rename the first column to "Time"
data$X.1 <- NULL # remove empty column
head(data) # check whether reading in went well

# Set subject number
subject <- "32" # !!ADAPT!!
```

&nbsp;

#### Check electrodes
```{r}
# Save electrodenames in a vector
electrodeNames <- colnames(data)
electrodeNames <- electrodeNames[! electrodeNames %in% "Time"]
length(electrodeNames) # should be 62 minus [number of rejected channels] in the 'bad channels' tab of the preprocessing info

```

&nbsp;

#### Add trial variable
```{r}
# variables (adjust according to your own data parameters)
samplingrate <- 1/100  # data has been downsampled to 100 Hz during preprocessing
lsegment <- 1400/1000  # segments from -200 to 1200 ms around target onset, so epochs of 1400 ms


# eeg: check number of trials and data points
print(ntrials <- dim(data)[1]/(lsegment/samplingrate)) #should be nr. of trials minus rejected trials
print(datapoints <- as.numeric(nrow(data))) 
print(datapoints.pertrial <- datapoints/ntrials) # 140 data points per trial is correct, because each segment is 1400 ms long (ranging from -200 till 1200)
print(length.segment <- datapoints.pertrial*samplingrate) #should be 1.4 --> klopt

# add trial number
Trial <- as.data.frame(rep(1:216, each=(lsegment/samplingrate))) # create a dataframe with the total of 216 trial numbers
colnames(Trial)[1] <- "TrialNr" # rename the trial number variable
```

&nbsp;

#### Remove trials that were rejected ==> ADAPT FOR EACH PARTICIPANT!!
```{r}
Trial <- as.data.frame(Trial[! Trial$TrialNr %in% c("65","131","213"),]) # delete trial numbers of the trials that have been rejected
colnames(Trial)[1] <- "TrialNr" # rename trial number variable
data2 <- cbind(Trial, data)
```

&nbsp;

#### Restructure data 
```{r}
library(reshape)

data3 <- melt(data2, id.vars = c("TrialNr", "Time"))
colnames(data3) <- c("TrialNr", "Time", "Electrode", "mV")

```


&nbsp;

#### Add participant info ==> ADAPT FOR EACH PARTICIPANT!!
```{r}
# Add participant number
data3$Subject <- subject # !!ADAPT!!

# Add participant age
data3$Age <-61  # !!ADAPT!!
```

&nbsp;

#### Add Experiment Builder data --> ADAPT FOR EACH PARTICIPANT!!
```{r}
# Read behavioral data
EB <- read.delim("./EB data/0032/RESULTS_FILE.txt", header = T) # !!ADAPT!!

# Merge EB data with EEG data
complete <- merge(data3, EB, by.x = 'TrialNr', by.y = 'TRIAL_INDEX') # match the rows in both documents on trial number
#head(complete)
```

&nbsp;

#### Check responses to offline questions
```{r}
str(EB$RESPONSE) # check variable class for 'RESPONSE'
print(nrow(EB[EB$RESPONSE %in% "correct",]) + nrow(EB[EB$RESPONSE %in% "incorrect",])) # check if correct and incorrect responses add up to 54

# Calculate percentage correct responses
response <- droplevels(EB[! EB$RESPONSE %in% '.',]) # only select trials that involved a question
nrow(response) # check if participant responded to each of the 54 trials that were followed by a question --> should be 54

correct <- droplevels(response[response$RESPONSE %in% 'correct',]) # only select trials to which ptc responded correctly
nrow(correct)/nrow(response)*100 # calculate percentage of correct responses
```

&nbsp;

#### Remove irrelevant information trials
```{r}
# Remove control trials
experimental <- droplevels(complete[complete$senttype %in% 'exp',])

# Remove irrelevant columns
final <- subset(experimental, select = c(Subject, Age, TrialNr, Time, mV, Electrode, item, order, critword))

# Change the order of the columns
col_order <- c("Subject", "Age", "TrialNr", "Time", "item", "order", "critword", "Electrode", "mV")
final <- final[, col_order]

# Order the data
finalO <- final[order(final$Trial, final$Time, final$item, final$Electrode), ]

# Count number of trials included for analysis
included <- length(unique(finalO$Trial))
print(paste(included, "out of 162 trials are included for analysis"))
```

&nbsp;

#### Save dataframe with complete dataset
```{r}
# Save dataframe
save(finalO, file=paste("./Preprocessing_persubject_epochICA/",subject,"_epochICA.rdat", sep="")) 

# Print for which participant the data is saved
print(paste(subject,"_epochICA_rdat file is saved in ./Preprocessing_persubject_epochICA/", sep=" "))

```

