---
title: "WordOrderStudy_TOPOanalysis"
author: "Amélie la Roi"
date: "March 23, 2020"
output: html_document
---

Last update: March 23, 2020


```{r}
library(itsadug)
library(mgcv)
library(plyr)
library(eegkit)
library(ggplot2)
```


# Load data 
```{r}
# Save data between 300-400 ms
datadir <- "./Preprocessing_persubject_epochICA/"
allfiles <- dir(path=datadir)
dat <- c()

# Load and save data from all participants for all electrodes
for(i in allfiles ){
  print(i)
  load(sprintf("%s/%s", datadir, i))

  subdat <- droplevels(finalO[finalO$Time >= 300 & finalO$Time <= 400,])
  dat <- rbind(dat, subdat)
  subdat <- NULL
}


save(dat, file="./R output/allEl_300-400.rda", compress="xz")
```

# Add electrode locations
```{r}
# Load electrode locations
data("eegcoord") # r package eegkit

# Make column with electrode names
eegcoord$Electrode <- rownames(eegcoord)
eegcoord$Electrode <- as.factor(eegcoord$Electrode)

# Convert Electrode column in EEG df to upper case
levels(dat$Electrode) # check electrode names before converting
dat$Electrode <- toupper(dat$Electrode)
dat$Electrode <- as.factor(dat$Electrode)
str(dat) # check if Electrode is a factor again
levels(dat$Electrode) # check electrode names after converting

# Merge electrode locations with voltages
dat2 <- merge(dat, eegcoord, by = 'Electrode') # contains less rows than dat, so something is missing

# Check which electrodes are not in the eegcoord data
nas <- droplevels(dat2[is.na(dat2$x),]) # 190465 rows, corresponds to nrows(dat)-nrows(dat2)
                                          # O9 & O10 are not in eegcoord data

# Check positions of electrodes in eegcoord data
eegcap(eegcoord$Electrode) # O9 and O10 correspond to I1 and I2 in the eegcoord data, respectively

# Rename electrodes in eegcoord data
levels(dat$Electrode)[levels(dat$Electrode)=="O9"] <- "I1"
levels(dat$Electrode)[levels(dat$Electrode)=="O10"] <- "I2"

# Merge electrode data
dat2 <- merge(dat, eegcoord, by = 'Electrode') # dat2 now has same amount of rows as dat, so it worked
head(dat2) # check data
eegcap(levels(dat2$Electrode), type='2d', cex.label=1, col.label='black')
```

# Calculate averages
```{r}
# Calculate subject averages
avgElMean <- ddply(dat2, c("Subject", "Age", "order", "critword", "Electrode", "x", "y", "z", "xproj", "yproj"), summarise,
             subj.mV.median = median(mV, na.rm=TRUE),
             subj.mV = mean(mV, na.rm=TRUE),
             subj.mV = mean(mV, na.rm=TRUE),
             subj.n = length(mV[!is.na(mV)]))

# Make sure variables are factors
avgElMean$Subject <- as.factor(avgElMean$Subject)
avgElMean$order <- as.factor(avgElMean$order)
avgElMean$critword <- as.factor(avgElMean$critword)
avgElMean$Event <- interaction(avgElMean$Subject, avgElMean$order, avgElMean$critword, drop=TRUE)


# Check number of data points to select gam (< 10000) or bam (> 10000)
dim(avgElMean) # more than 10000 data points, so use bam

# Save the data for use in Peregrine
save(avgElMean,file="./R output/avgElMean.rda", compress="xz")

# Make subset data for verb-final and verb-first sentence
datElSOV <- droplevels(avgElMean[avgElMean$order == "verb-final",])
datElSVO <- droplevels(avgElMean[avgElMean$order == "verb-first",])

# Save data for later use in Peregrine
save(datElSOV, file="./R output/datElSOV.rda", compress="xz")
save(datElSVO, file="./R output/datElSVO.rda", compress="xz")


```

# SOV SENTENCES
## Fit model for rho value
```{r, fig.height=5, fig.width=5}
# Basic model
m0.el <- bam(subj.mV ~ te(x, y), data=datElSOV)
plot_topo(m0.el, view=c("x", "y"))
```


# Add electrodes
```{r}
electrodes <- datElSOV[,c('x','y','Electrode')]
electrodes <- as.list( electrodes[!duplicated(electrodes),] )

```

# Create binary predictors and ordered factors
```{r, message=FALSE, fig.height=20, fig.width=10}
# Binary predictors
datElSOV$IsCorrect <- ifelse(datElSOV$critword=="correct", 1,0)
datElSOV$IsLiteral <- ifelse(datElSOV$critword=="literal", 1,0)
datElSOV$IsUnrelated <- ifelse(datElSOV$critword=="unrelated", 1,0)

# Ordered factors
datElSOV$CritCor <- as.ordered(datElSOV$critword == 'correct')
contrasts(datElSOV$CritCor) <- "contr.treatment"
datElSOV$CritLit <- as.ordered(datElSOV$critword == 'literal')
contrasts(datElSOV$CritLit) <- "contr.treatment"
datElSOV$CritUnrel <- as.ordered(datElSOV$critword == 'unrelated')
contrasts(datElSOV$CritUnrel) <- "contr.treatment"

# Save data for later use in Peregrine
save(datElSOV, file="./R output/datElSOV.rda", compress="xz")

```

# Fit model with separate main effect and interaction effect
```{r}
# Fit full model
if(FALSE){
m1.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + s(Age, by=critword)
              + ti(x, y, Age, d=c(2,1), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m1.el.rda"))}

# Print model summary
(smry_m1.el <- summary(m1.el)) # no main effect of Age

# Fit model without main effect Age
if(FALSE){
m2.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + ti(x, y, Age, d=c(2,1), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m2.el.rda"))}

# Print model summary
(smry_m2.el <- summary(m2.el)) 

# Compare models
compareML(m1.el, m2.el, suggest.report = TRUE)

# Check model fit
gam.check(m2.el)
```

# Increase k for interaction
```{r}
# Fit model with increased k
if(FALSE){
m3.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + ti(x, y, Age, d=c(2,1), k=c(5,5,20), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m3.el.rda"))}

# Print model summary
(smry_m3.el <- summary(m3.el))

# Check model fit
gam.check(m3.el) # increasing k does not help, so keep at standard (m2.el)
```



# Binary model with separate main effect and interaction effect
```{r}
# Fit model without main effect Age
if(FALSE){
m2.elBinLit <- bam(subj.mV ~ s(x, y)
              + s(x, y, by=IsCorrect)
              + s(x, y, by=IsUnrelated)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=IsCorrect)
              + ti(x, y, Age, d=c(2,1), by=IsUnrelated)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m2.elBinLit.rda"))}

# Print model summary
(smry_m2.elBinLit <- summary(m2.elBinLit)) 

# Fit model with correct as reference level
if(FALSE){
m2.elBinCor <- bam(subj.mV ~ s(x, y)
              + s(x, y, by=IsLiteral)
              + s(x, y, by=IsUnrelated)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=IsLiteral)
              + ti(x, y, Age, d=c(2,1), by=IsUnrelated)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m2.elBinCor.rda"))}

# Print model summary
(smry_m2.elBinCor <- summary(m2.elBinCor))

# Report statistics
(report_m2.elBinLit <- report_stats(m2.elBinLit))
(report_m2.elBinCor <- report_stats(m2.elBinCor))
```

# Fit model with ordered factors
```{r}
# Reference level literal
if(FALSE){
m2.elOrdLit <- bam(subj.mV ~ CritCor + CritUnrel
              + s(x, y)
              + s(x, y, by=CritCor)
              + s(x, y, by=CritUnrel)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=CritCor)
              + ti(x, y, Age, d=c(2,1), by=CritUnrel)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m2.elOrdLit.rda"))}

# Print model summary
(smry_m2.elOrdLit <- summary(m2.elOrdLit))

# Reference level correct
if(FALSE){
m2.elOrdCor <- bam(subj.mV ~ CritLit + CritUnrel
              + s(x, y)
              + s(x, y, by=CritLit)
              + s(x, y, by=CritUnrel)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=CritLit)
              + ti(x, y, Age, d=c(2,1), by=CritUnrel)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSOV, discrete = FALSE, method="ML")
}else{print(load("./Models/m2.elOrdCor.rda"))}

# Print model summary
(smry_m2.elOrdCor <- summary(m2.elOrdCor))

```


# Plot distributional differences between conditions averaged over all participants
```{r, echo=FALSE, fig.height=5, fig.width=15}
par(mfrow=c(1,3))
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SOV\nUnrelated vs. correct')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SOV\nUnrelated vs. literal')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SOV\nLiteral vs. correct')

```

# Compare distributional differences between conditions across age
```{r, echo=FALSE, fig.height=35, fig.width=15}
par(mfcol=c(3,7))
## Age=20
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SOV\nUnrelated vs. correct\nAge=20')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SOV\nUnrelated vs. literal\nAge=20')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SOV\nLiteral vs. correct\nAge=20')

## Age=30
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SOV\nUnrelated vs. correct\nAge=30')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SOV\nUnrelated vs. literal\nAge=30')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SOV\nLiteral vs. correct\nAge=30')

## Age=40
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SOV\nUnrelated vs. correct\nAge=40')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SOV\nUnrelated vs. literal\nAge=40')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SOV\nLiteral vs. correct\nAge=40')

## Age=50
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SOV\nUnrelated vs. correct\nAge=50')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SOV\nUnrelated vs. literal\nAge=50')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SOV\nLiteral vs. correct\nAge=50')

## Age=60
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SOV\nUnrelated vs. correct\nAge=60')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SOV\nUnrelated vs. literal\nAge=60')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SOV\nLiteral vs. correct\nAge=60')

## Age=70
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SOV\nUnrelated vs. correct\nAge=70')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SOV\nUnrelated vs. literal\nAge=70')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SOV\nLiteral vs. correct\nAge=70')

## Age=80
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SOV\nUnrelated vs. correct\nAge=80')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SOV\nUnrelated vs. literal\nAge=80')
plot_topo(m2.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SOV\nLiteral vs. correct\nAge=80')
```


# SVO SENTENCES
## Fit model for rho value
```{r, fig.height=5, fig.width=5}
# Basic model
m02.el <- bam(subj.mV ~ te(x, y), data=datElSVO)
plot_topo(m02.el, view=c("x", "y"))
```


# Add electrodes
```{r}
electrodes <- datElSVO[,c('x','y','Electrode')]
electrodes <- as.list( electrodes[!duplicated(electrodes),] )

```



# Plot differences between critword conditions
```{r, echo=FALSE, fig.height=5, fig.width=15}
# Extract electrode positions
electrodes <- dat2[,c('x','y','Electrode')]
electrodes <- as.list( electrodes[!duplicated(electrodes),] )

```

# Create binary predictors and ordered factors
```{r, message=FALSE, fig.height=20, fig.width=10}
datElSVO$IsCorrect <- ifelse(datElSVO$critword=="correct", 1,0)
datElSVO$IsLiteral <- ifelse(datElSVO$critword=="literal", 1,0)
datElSVO$IsUnrelated <- ifelse(datElSVO$critword=="unrelated", 1,0)

# Ordered factors
datElSVO$CritCor <- as.ordered(datElSVO$critword == 'correct')
contrasts(datElSVO$CritCor) <- "contr.treatment"
datElSVO$CritLit <- as.ordered(datElSVO$critword == 'literal')
contrasts(datElSVO$CritLit) <- "contr.treatment"
datElSVO$CritUnrel <- as.ordered(datElSVO$critword == 'unrelated')
contrasts(datElSVO$CritUnrel) <- "contr.treatment"

# Save data for later use in Peregrine
save(datElSVO, file="./R output/datElSVO.rda", compress="xz")


```


# Fit model with separate main effect and interaction effect
```{r}
# Fit full model
if(FALSE){
m12.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + s(Age, by=critword)
              + ti(x, y, Age, d=c(2,1), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m12.el.rda"))}

# Print model summary
(smry_m12.el <- summary(m12.el)) # no main effect of Age

# Fit model without main effect Age
if(FALSE){
m22.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + ti(x, y, Age, d=c(2,1), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m22.el.rda"))}

# Print model summary
(smry_m22.el <- summary(m22.el)) 

# Compare models
compareML(m12.el, m22.el, suggest.report = TRUE)

# Check model fit
gam.check(m22.el)
```

# Increase k for interaction
```{r}
# Fit model with increased k
if(FALSE){
m32.el <- bam(subj.mV ~ critword 
              + s(x, y, by=critword)
              + ti(x, y, Age, d=c(2,1), k=c(5,5,20), by=critword)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = TRUE)
}else{print(load("./Models/m32.el.rda"))}

# Print model summary
(smry_m32.el <- summary(m32.el))

# Check model fit
gam.check(m32.el) # increasing k does not help, so keep at standard (m2.el)
```

# Binary model with separate main effect and interaction effect
```{r}
# Fit model without main effect Age
if(FALSE){
m22.elBinLit <- bam(subj.mV ~ s(x, y)
              + s(x, y, by=IsCorrect)
              + s(x, y, by=IsUnrelated)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=IsCorrect)
              + ti(x, y, Age, d=c(2,1), by=IsUnrelated)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m22.elBinLit.rda"))}

# Print model summary
(smry_m22.elBinLit <- summary(m22.elBinLit)) 

# Fit model with correct as reference level
if(FALSE){
m22.elBinCor <- bam(subj.mV ~ s(x, y)
              + s(x, y, by=IsLiteral)
              + s(x, y, by=IsUnrelated)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=IsLiteral)
              + ti(x, y, Age, d=c(2,1), by=IsUnrelated)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m22.elBinCor.rda"))}

# Print model summary
(smry_m22.elBinCor <- summary(m22.elBinCor)) 

# Report statistics
(report_m22.elBinLit <- report_stats(m22.elBinLit))
(report_m22.elBinCor <- report_stats(m22.elBinCor))
```

# Fit model with ordered factors
```{r}
# Reference level literal
if(FALSE){
m22.elOrdLit <- bam(subj.mV ~ CritCor + CritUnrel
              + s(x, y)
              + s(x, y, by=CritCor)
              + s(x, y, by=CritUnrel)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=CritCor)
              + ti(x, y, Age, d=c(2,1), by=CritUnrel)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m22.elOrdLit.rda"))}

# Print model summary
(smry_m22.elOrdLit <- summary(m22.elOrdLit))

# Reference level correct
if(FALSE){
m22.elOrdCor <- bam(subj.mV ~ CritLit + CritUnrel
              + s(x, y)
              + s(x, y, by=CritLit)
              + s(x, y, by=CritUnrel)
              + ti(x, y, Age, d=c(2,1))
              + ti(x, y, Age, d=c(2,1), by=CritLit)
              + ti(x, y, Age, d=c(2,1), by=CritUnrel)
              + s(Age, Electrode, bs="fs", m=1),
              data=datElSVO, discrete = FALSE, method="ML")
}else{print(load("./Models/m22.elOrdCor.rda"))}

# Print model summary
(smry_m22.elOrdCor <- summary(m22.elOrdCor))

```

# Plot distributional differences between conditions averaged over all participants
```{r, echo=FALSE, fig.height=5, fig.width=15}
par(mfrow=c(1,3))
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SVO\nUnrelated vs. correct')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SVO\nUnrelated vs. literal')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), main='SVO\nLiteral vs. correct')

```

# Compare distributional differences between conditions across age
```{r, echo=FALSE, fig.height=35, fig.width=15}
par(mfcol=c(3,7))
## Age=20
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SVO\nUnrelated vs. correct\nAge=20')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SVO\nUnrelated vs. literal\nAge=20')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=20), main='SVO\nLiteral vs. correct\nAge=20')

## Age=30
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SVO\nUnrelated vs. correct\nAge=30')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SVO\nUnrelated vs. literal\nAge=30')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=30), main='SVO\nLiteral vs. correct\nAge=30')

## Age=40
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SVO\nUnrelated vs. correct\nAge=40')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SVO\nUnrelated vs. literal\nAge=40')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=40), main='SVO\nLiteral vs. correct\nAge=40')

## Age=50
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SVO\nUnrelated vs. correct\nAge=50')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SVO\nUnrelated vs. literal\nAge=50')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=50), main='SVO\nLiteral vs. correct\nAge=50')

## Age=60
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SVO\nUnrelated vs. correct\nAge=60')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SVO\nUnrelated vs. literal\nAge=60')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=60), main='SVO\nLiteral vs. correct\nAge=60')

## Age=70
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SVO\nUnrelated vs. correct\nAge=70')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SVO\nUnrelated vs. literal\nAge=70')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=70), main='SVO\nLiteral vs. correct\nAge=70')

## Age=80
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SVO\nUnrelated vs. correct\nAge=80')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('unrelated', 'literal')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SVO\nUnrelated vs. literal\nAge=80')
plot_topo(m22.el, view=c('x', 'y'), comp=list(critword=c('literal', 'correct')), color='terrain',
    el.pos=electrodes, fun='plot_diff2', zlim=c(-1,1), cond=list(Age=80), main='SVO\nLiteral vs. correct\nAge=80')
```
